Nonlinear methods to quantify Movement Variability in Human-Humanoid Interaction Activities

### 2021-03-15 docs/manuscript/main.tex
polishes README.md; polishes coverletter; updates abstracts and re-submit to arxiv with v04
fused fig1,2,3 into fig01

\includegraphics[width=1.0\textwidth]{figures/methods/rss/pdf/rss}

@@

@@

%%---------------------------------(FIGURE)-------------------------------------
\begin{figure}[ht]
\centering
\includegraphics[width=1.0\textwidth]{figures/methods/caoami/versions/drawing-v00.pdf}
    \caption{
	{\bf Minimum delay embedding values with AMI's method and minimum dimension embedding values with Cao's method.} 
	(A) chaotic and (B) random time series.
	(C, D) $E_1 (m)$ values and (E, F) $E_2(m)$ values 
	with variations of $\tau$ values from one to twenty
	for chaotic and random time series.
	(G, H) AMI values where its first minimum value in the curve
	is the minimum time delay embedding ($\tau_0$).
	Code and data to reproduce the figure is available in \cite{srep2020}.
        }
    \label{fig:caoami}
\end{figure}
%%---------------------------------(FIGURE)-------------------------------------

@@

%---------------------------------(FIGURE)-------------------------------------
\begin{figure}[ht]
\centering
\includegraphics[width=1.0\textwidth]{figures/methods/rps/versions/drawing-v00.pdf}
    \caption{
	{\bf Recurrence Plots and its patterns.} 
	(A) State space of the Lorenz system with controlling parameters 
	($\rho=28, \sigma=10, \beta=8/3$) where the point, $j$, in trajectory $X()$ which falls into the neighborhood 
	(black circle) of a given point at $i$ is a recurrent point and is 
	represented as a black dot in the recurrence plot at location 
	$(i, j)$ or white otherwise.
	(B) Recurrence plot using the 
	three components of the Lorenz system and the RP with no embeddings 
	and threshold $\epsilon=5$.
	Time-series with its respective recurrence plot for:
	(C) uniformly distributed noise,
	(D) super-positionet harmonic oscillation 
	($sin( \frac{1}{5}*t) * sin( \frac{5}{100}*t) $),
	(E) drift logistic map ($x_{i+1} = 4 x_i (1- x_i) $) corrupted 
	with a linearly increase term ($0.01*i$), and
	(F) disrupted brownian motion  ($x_{i+1} = x_i + 2*rnorm(1) $).
	This figure is adapted from \cite{marwan2015}.
	Code and data to reproduce the figure is available in \cite{srep2020}.
	}
    \label{fig:rps}
\end{figure}
%%---------------------------------(FIGURE)-------------------------------------

@@

\subsection*{Recurrences Plots}
Using the average embedding parameters 
($\overline{m}_0=6$, $\overline{\tau}_0=8$) 
and an recurrence threshold of $\epsilon=1$.
As our interest is for dynamical transitions, 
there is little importance on the selection of $\epsilon$ which in this case
is 1. 
Recurrence Plots (RP) were computed for horizontal (figures~\ref{fig:rps}(A)) and 
vertical (figures~\ref{fig:rps}(B)) arm movements.
%%---------------------------------(FIGURE)-------------------------------------
\begin{figure}[ht]
\centering
\includegraphics[width=1.0\textwidth]{figures/rps/versions/drawing-v00.pdf}
\caption{
	{\bf RPs for horizontal (A) and vertical (B) arm movements.}	
	Recurrence plots were computed with 
	embedding parameters 
	$\overline{m}_0=6$, $\overline{\tau}_0=8$, and $\epsilon=1$.
	Code and data to reproduce the figure is available in \cite{srep2020}.
        }
    \label{fig:rps}
\end{figure}
%%---------------------------------(FIGURE)------------------------------------

>>>>

\includegraphics[width=1.0\textwidth]{figures/fig01/versions/drawing-v00}

@@

	{\bf Minimum delay embedding values with AMI's method and minimum dimension embedding values with Cao's method.} 
	(A) chaotic and (B) random time series.
	(C, D) $E_1 (m)$ values and (E, F) $E_2(m)$ values 
	with variations of $\tau$ values from one to twenty
	for chaotic and random time series.
	(G, H) AMI values where its first minimum value in the curve
	is the minimum time delay embedding ($\tau_0$).
	{\bf Recurrence Plots and its patterns.} 
	(A) State space of the Lorenz system with controlling parameters 
	($\rho=28, \sigma=10, \beta=8/3$) where the point, $j$, in trajectory $X()$ which falls into the neighborhood 
	(black circle) of a given point at $i$ is a recurrent point and is 
	represented as a black dot in the recurrence plot at location 
	$(i, j)$ or white otherwise.
	(B) Recurrence plot using the 
	three components of the Lorenz system and the RP with no embeddings 
	and threshold $\epsilon=5$.
	Time-series with its respective recurrence plot for:
	(C) uniformly distributed noise,
	(D) super-positionet harmonic oscillation 
	($sin( \frac{1}{5}*t) * sin( \frac{5}{100}*t) $),
	(E) drift logistic map ($x_{i+1} = 4 x_i (1- x_i) $) corrupted 
	with a linearly increase term ($0.01*i$), and
	(F) disrupted brownian motion  ($x_{i+1} = x_i + 2*rnorm(1) $).
	This figure is adapted from \cite{marwan2015}.

@@

%%%---------------------------------(FIGURE)-------------------------------------
%\begin{figure}[ht]
%\centering
%\includegraphics[width=1.0\textwidth]{figures/methods/caoami/versions/drawing-v00.pdf}
%    \caption{
%	{\bf Minimum delay embedding values with AMI's method and minimum dimension embedding values with Cao's method.} 
%	(A) chaotic and (B) random time series.
%	(C, D) $E_1 (m)$ values and (E, F) $E_2(m)$ values 
%	with variations of $\tau$ values from one to twenty
%	for chaotic and random time series.
%	(G, H) AMI values where its first minimum value in the curve
%	is the minimum time delay embedding ($\tau_0$).
%	Code and data to reproduce the figure is available in \cite{srep2020}.
%        }
%    \label{fig:caoami}
%\end{figure}
%%---------------------------------(FIGURE)-------------------------------------

@@

%%---------------------------------(FIGURE)-------------------------------------
%\begin{figure}[ht]
%\centering
%\includegraphics[width=1.0\textwidth]{figures/methods/rps/versions/drawing-v00.pdf}
%    \caption{
%	{\bf Recurrence Plots and its patterns.} 
%	(A) State space of the Lorenz system with controlling parameters 
%	($\rho=28, \sigma=10, \beta=8/3$) where the point, $j$, in trajectory $X()$ which falls into the neighborhood 
%	(black circle) of a given point at $i$ is a recurrent point and is 
%	represented as a black dot in the recurrence plot at location 
%	$(i, j)$ or white otherwise.
%	(B) Recurrence plot using the 
%	three components of the Lorenz system and the RP with no embeddings 
%	and threshold $\epsilon=5$.
%	Time-series with its respective recurrence plot for:
%	(C) uniformly distributed noise,
%	(D) super-positionet harmonic oscillation 
%	($sin( \frac{1}{5}*t) * sin( \frac{5}{100}*t) $),
%	(E) drift logistic map ($x_{i+1} = 4 x_i (1- x_i) $) corrupted 
%	with a linearly increase term ($0.01*i$), and
%	(F) disrupted brownian motion  ($x_{i+1} = x_i + 2*rnorm(1) $).
%	This figure is adapted from \cite{marwan2015}.
%	Code and data to reproduce the figure is available in \cite{srep2020}.
%	}
%    \label{fig:rps}
%\end{figure}
%%%---------------------------------(FIGURE)-------------------------------------

@@

\subsection*{Recurrences Plots}
Using the average embedding parameters 
($\overline{m}_0=6$, $\overline{\tau}_0=8$) 
and an recurrence threshold of $\epsilon=1$.
As our interest is for dynamical transitions, 
there is little importance on the selection of $\epsilon$ which in this case
is 1. 
Recurrence Plots (RP) were computed for horizontal (figures~\ref{fig:rpsr}(A)) and 
vertical (figures~\ref{fig:rpsr}(B)) arm movements.
%%---------------------------------(FIGURE)-------------------------------------
\begin{figure}[ht]
\centering
\includegraphics[width=1.0\textwidth]{figures/rps/versions/drawing-v00.pdf}
\caption{
	{\bf RPs for horizontal (A) and vertical (B) arm movements.}	
	Recurrence plots were computed with 
	embedding parameters 
	$\overline{m}_0=6$, $\overline{\tau}_0=8$, and $\epsilon=1$.
	Code and data to reproduce the figure is available in \cite{srep2020}.
        }
    \label{fig:rpsr}
\end{figure}
%%---------------------------------(FIGURE)------------------------------------
